Smart Drill-Down

### 2015-10-17 TableSummarization/Paper/algorithms.tex
almost at length

\For {$i$ from $1$ to $k$}{
$R_m = \text{Find\_best\_marginal\_rule}(S, T, m_w, W)$ \tcc*{Calling Algorithm~\ref{algo:best-marginal-rule}}

@@

We now describe the function to find the best marginal rule. The pseudo-code for the function is in the box titled Algorithm~\ref{algo:best-marginal-rule}. The function maintains a threshold $H$, which is the highest marginal value that has been found for any rule so far. The function makes several iterations (Step $3$), counting marginal values for size $j$ rules in the $j^{th}$ iteration. We maintain three sets of rules. $C$ is the set of all rules whose marginal values have been counted in all previous iterations. $C_n$ is the set of rules whose marginal values are going to be counted in the current pass. And $C_o$ is the set of rules whose marginal values were counted in the previous iteration. For the first pass, we set $C_n$ to be all rules of size $1$. Then we compute marginal values for those rules, and set $C = C_o = C_n$.

>>>>

\For {$i$ from $1$ to $k$}{
$R_m = \text{Find\_best\_marginal\_rule}(S, T, m_w, W)$

@@

We now describe the function to find the best marginal rule. \papertext{The pesudo-code for the function is in the technical report}\techreporttext{The pseudo-code for the function is in the box titled Algorithm~\ref{algo:best-marginal-rule}}. The function maintains a threshold $H$, which is the highest marginal value that has been found for any rule so far. The function makes several iterations (Step $3$), counting marginal values for size $j$ rules in the $j^{th}$ iteration. We maintain three sets of rules. $C$ is the set of all rules whose marginal values have been counted in all previous iterations. $C_n$ is the set of rules whose marginal values are going to be counted in the current pass. And $C_o$ is the set of rules whose marginal values were counted in the previous iteration. For the first pass, we set $C_n$ to be all rules of size $1$. Then we compute marginal values for those rules, and set $C = C_o = C_n$.
